MaxEnt: What is it good for?

### 2015-06-15 ms.tex
People use it to justify priors

The principle of maximum entropy (MaxEnt) is an idea in probability theory
that is usually associated with \citet{jaynes}. The principle may be used
to {\it assign} or {\it update} a
subjective\footnote{in the sense that the probability distribution is a model
of the state of uncertainty of an idealised rational agent, rather than
a {\it frequency distribution} such as a histogram of people's heights.}
probability distribution when you obtain a certain kind of information
called {\it testable information}. The principle is very intuitively compelling
and there are some axiomatic arguments in its favour
\citep[e.g.][]{2010arXiv1008.4831K}. However, MaxEnt has also been widely
misapplied (even by some of its staunchest defenders), misunderstood,
and poorly defended (even by Jaynes himself).

>>>>

The principle of maximum entropy (MaxEnt) is an idea in probability theory
that is usually associated with \citet{jaynes}. The principle may be used
to {\it assign} or {\it update} a
subjective\footnote{in the sense that the probability distribution is a model
of the state of uncertainty of an idealised rational agent, rather than
a {\it frequency distribution} such as a histogram of people's heights.}
probability distribution when you obtain a certain kind of information
called {\it testable information}. The principle is very intuitively compelling
and there are some axiomatic arguments in its favour
\citep[e.g.][]{2010arXiv1008.4831K}. However, MaxEnt has also been widely
misapplied (even by some of its staunchest defenders), misunderstood,
and poorly defended (at times, even by Jaynes himself).
Consequently, most modern Bayesians pay little attention to the principle,
although there is a tendency among physicists to invoke it as a justification
for a prior distribution (be it uniform, exponential, gaussian, or whatever).
